### 2019-03-10 manuscript/discussion.tex
read through Results
- outline in discussion, removed errant mark in main
- first paragraph of Discussion

@@

>>>>

% outline
% - disentangling effects
% - general value of approach
%  		another kind of confounding processes, not only transition and diversification, but "other diversifications" and "other transitions", esp. correlated
%
% - our study key findings and details
% - effects of Ploidy (as %R)
% - trumped by BS
% - no difference on background of SC 
% - discuss data/models and their long/shortcomings: ClaSSE, will's idea for stochastic mapping
% - how to improve / what next
%  (may be useful to study in SC families)
%
% - pathways
% 
%- diploidization
% - rate, effect
% - history in solanaceae
%
% - summary

We investigated the individual and joint effects of ploidy and breeding system states in diversification of Solanaceae.
Most significantly, we found that the effects of ploidy, inferred as significant when it is the only trait under consideration, are trumped by breeding systems when the two traits are considered jointly.
Interestingly, the difference in diversification rates between the diploids and polyploids is negligible on the background of self-compatibility.
%B: should we mention here that the hidden states presage these results in each case? Maybe we don't want to make too much of that, but it is fairly interesting. Also possibly hit that in your paragraph(s), below.
In the same vein, the difference in diversification rates between self-incompatible and self-compatible lineages is smaller in the diploid genomic background.
In our final analyses, motivated by the widespread findings of paleopolyploid ancestry across angiosperms, we did not recover strong support for inclusion of diploidization process.
Below, we discuss the key findings, and outline a broad strategy for applying phylogenetic comparative methods in the study of complex interactions among traits, in the context of diversification.
%  Surprising outcomes: (1)  D and P on background of C, and (2) SC not as dead of an end as it was in goldberg2010, if P is partitioned out (can be framed as kind of path-dependence, i.e. qIC path different than rho path, or same as (1), so that I and C are less different on the background of D.

@@

% And, are diversification rates of polyploid SC lineages different if one or other path was taken? \citet{charlesworth1985} % E: This is a great question.  We don't answer it with this round of analyses.  But discuss?
